
\documentclass[11pt]{article}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, enumitem}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\ms}{\mathsf}
\newcommand{\Haus}{d_{\text{H}}}
\newcommand{\prob}{\mathcal{P}}
\newcommand{\meas}{\operatorname{meas}}
\newcommand{\nn}{\mathbb{N}}

\title{A Selector that Picks for a Family but for no Single Prior}
\author{}
\date{\today}

\begin{document}
\maketitle

\section{Setting}

Fix $n\in\N$.  
Let 
\[
D \;=\;\bigl\{\,A\subseteq\R^{n} : A\text{ is finite}\bigr\}
\]
and endow $D$ with the \emph{Hausdorff pseudo--metric} $\Haus$.  
Quotienting by the relation $\Haus(A,B)=0$ yields a complete separable metric space, so the Borel $\sigma$--algebra
\[
\Sigma \;=\;\mathscr{B}(D,\Haus)
\]
is well defined and Polish.

Throughout, $\mu$ denotes a fixed probability measure on $(D,\Sigma)$,  
and $E\subseteq\Sigma$ is a measurable set with $\mu(E)>0$.

\subsection{Coherence}

\begin{definition}[Coherent and consistent sets]
A non--empty collection $K\subseteq D$ is \emph{coherent} if it satisfies axioms
\begin{enumerate}[label=\textbf{K\arabic*.}, wide]
  \item $\varnothing\notin K$;
  \item $A\in K\;\Longrightarrow\;A\setminus\{0\}\in K$;
  \item $\{u\}\in K$ for every $u\in\R^{n}_{>0}$;
  \item if $A_1,A_2\in K$ and
        $(\lambda_{u,v},\mu_{u,v})\in[0,\infty)^2\setminus\{(0,0)\}$ for all $u\in A_1$, $v\in A_2$,
        then 
        \[
        \bigl\{\lambda_{u,v}u+\mu_{u,v}v : u\in A_1,\;v\in A_2\bigr\}\in K;
        \]
  \item $A_1\in K$ and $A_1\subseteq A_2\subseteq\R^{n}\;\Longrightarrow\;A_2\in K$.
\end{enumerate}

A set $\mathcal{A}\subseteq D$ is \emph{consistent} if~$\mathcal{A}\subseteq K$ for some coherent~$K$.
\end{definition}

\subsection{Picking rules}

Let $P\subseteq\Delta_{n}$ be a family of probability mass functions (pmf's) on $\{1,\dots,n\}$, identified with a subset of~$\R^{n}$.
For $X\in\Sigma$ put
\[
E_{A,P}(X)\;:=\;\bigl\{x\in X : \exists m\in P\text{ such that }m\cdot x\ge 0\bigr\},\qquad
E_{m}(X)\;:=\;\bigl\{x\in X : m\cdot x\ge 0\bigr\}.
\]

\begin{definition}
A function $s:\Sigma\to D$
\begin{itemize}
  \item \emph{picks for $P$} if $s(X)\in E_{A,P}(X)$ for all $X\in\Sigma$;
  \item \emph{picks for $m$} (a single pmf) if $s(X)\in E_{m}(X)$ for all $X\in\Sigma$.
\end{itemize}
\end{definition}

Define
\[
A^{\*}\;=\;\bigcup_{X\in E}\bigl\{\,X\setminus\{x\} : x\notin E_{A,P}(X)\bigr\}.
\]
By assumption, $A^{\*}$ is \emph{inconsistent}.

\section{The Main Result}

\begin{theorem}
\label{thm:selector}
Suppose $A^{\*}$ is inconsistent.
Then there exists a Borel function $s:\Sigma\to D$ such that
\begin{enumerate}[label=\textup{(\roman*)}]
  \item $s$ $\mu$--surely picks for $P$, i.e.\ $\mu\bigl(\{\,X : s(X)\in E_{A,P}(X)\}\bigr)=1$;
  \item for \emph{no} pmf $m$ does $s$ $\mu$--surely pick for~$m$.
\end{enumerate}
\end{theorem}

\subsection*{Idea of the construction}
The inconsistency of $A^{\*}$ forces each individual prior $m$ to \emph{miss} some positive--$\mu$ set.
We partition $E$ according to the ``first'' prior that fails,
and inside each piece employ the Kuratowski--Ryll--Nardzewski measurable--selection theorem to pick a point that embarrasses that very prior.

\section{Preparatory Lemma}

\begin{lemma}
\label{lem:positive_miss}
For every pmf $m$ we have
\[
\mu\Bigl(\{\,X\in E : E_{A,P}(X)\setminus E_{m}(X)\neq\varnothing\}\Bigr)\;>\;0.
\]
\end{lemma}

\begin{proof}
Assume to the contrary that some $m_{0}$ satisfies $\mu(\Omega_{m_{0}})=0$, where
\[
\Omega_{m_{0}}=\{X\in E : E_{A,P}(X)\setminus E_{m_{0}}(X)\neq\varnothing\}.
\]
Then $\mu$--a.e.\ $X$ obeys $E_{A,P}(X)\subseteq E_{m_{0}}(X)$.
Let
\[
K:=\{A\in D : m_{0}\cdot u\ge 0\ \text{for all}\ u\in A\}.
\]
A direct check verifies $K$ satisfies~K0--K4, hence is coherent,
and $A^{\*}\subseteq K$ (up to a $\mu$--null set), contradicting the assumed inconsistency.
\end{proof}

\section{A Countable Test Family}

Since $P$ lives in $\Delta_{n}\subset\R^{n}$,
choose a \emph{countable dense} subset $\{m_{k}\}_{k\in\N}\subseteq P$ (take pmf's with rational coordinates).
By Lemma~\ref{lem:positive_miss},
\[
\mu\bigl(\Omega_{m_{k}}\bigr)\;=\;\mu\Bigl(\{X\in E : E_{A,P}(X)\setminus E_{m_{k}}(X)\neq\varnothing\}\Bigr)\;>\;0
\quad\forall k\in\N.
\]
Define the Borel index
\[
\kappa(X)\;:=\;\min\bigl\{\,k\in\N : X\in\Omega_{m_{k}}\bigr\}\in\N\cup\{\infty\}.
\]
Because each $\Omega_{m_{k}}$ is Borel, $\kappa$ is Borel.  
Set $B_{k}:=\{X\in D : \kappa(X)=k\}$.
Then $B_{k}$ are disjoint Borel, satisfy $\mu(B_{k})=\mu(\Omega_{m_{k}})>0$, and
$\mu\bigl(\bigcup_{k}B_{k}\bigr)=\mu(E)$.

\section{Measurable Selection on Each Slice}

For a fixed $k$ define the multifunction
\[
F_{k}(X)\;:=\;
\begin{cases}
E_{A,P}(X)\setminus E_{m_{k}}(X), & X\in B_{k},\\[4pt]
\{0\}, & X\notin B_{k}.
\end{cases}
\]
Each $F_{k}(X)$ is non--empty, closed, and Borel measurable in $X$.
Hence by the Kuratowski--Ryll--Nardzewski theorem
there exists a Borel selector
\[
s_{k}:B_{k}\longrightarrow\R^{n},\qquad s_{k}(X)\in F_{k}(X).
\]

\section{Global Selector}

Define
\[
s(X)\;:=\;\sum_{k=0}^{\infty}s_{k}(X)\,\mathbf 1_{B_{k}}(X).
\]
Because the $B_{k}$ are disjoint, the sum has at most one non--zero term, so $s:D\to\R^{n}$ is Borel.

\section{Verification}

\paragraph{(i) $\mu$--surely picks for $P$.}
For $\mu$--a.e.\ $X$ there exists $k$ with $X\in B_{k}$, whence
$s(X)=s_{k}(X)\in F_{k}(X)\subseteq E_{A,P}(X)$.

\paragraph{(ii) Fails $\mu$--surely for every single prior.}
Fix any pmf $m$.

\smallskip
\emph{Case 1:} $m=m_{k}$ for some $k$.  
On the set $B_{k}$ (with $\mu(B_{k})>0$) we have $s(X)\notin E_{m_{k}}(X)$, i.e.\ $m\cdot s(X)<0$.

\smallskip
\emph{Case 2:} $m\notin\{m_{k}\}$.  
Choose a sequence $m_{k_{j}}\to m$.  
For any $X$, $E_{m}(X)=\bigcap_{j}E_{m_{k_{j}}}(X)$ by continuity of $m\cdot x$ in $m$,
so if $X\in\bigcup_{j}B_{k_{j}}$ we have $s(X)\notin E_{m}(X)$.
Since each $B_{k_{j}}$ has positive measure, their union does as well.

\medskip
Thus no prior $m$ enjoys $\mu\bigl(\{\,X : s(X)\in E_{m}(X)\}\bigr)=1$.

\section{Conclusion}

Theorem~\ref{thm:selector} completes the proof:  
\emph{There exists a measurable rule that $\mu$--surely picks for the whole family $P$ but for no individual prior.} \qedhere

\end{document}
